Safety Analysis of the Molten Salt Fast Reactor Fuel Composition using Moltres

### 2019-03-15 abstract.tex
final final edits

In line with the purpose of the \gls{MSFR} as a thorium breeder, its chosen 
        start-up fuel composition is a eutectic mixture of $^{233}$U and 
        $^{232}$Th fluorides in a lithium fluoride molten salt 
        \cite{merle-lucotte_launching_2011}. We generate group constants for 
        each fuel composition using Serpent \cite{leppanen_serpent_2015}, a 
        continuous-energy Monte Carlo code for numerous reactor physics 
        applications. For verification, we will compare group constants and
        reactivity coefficients with existing data 
        \cite{fiorina_analysis_2012,fiorina_investigation_2013} of safety 
        parameters for the three fuel compositions.  
        Using these group constants ($\chi$, $\nu\Sigma_f$, 
        $\Sigma_{g\rightarrow g'}$, $\frac{d\rho}{dT}$, etc.), Moltres then 
        solves for the flux and temperature based on the neutron diffusion 
        equation coupled with navier stokes thermal hydraulics. Transient 
        simulations will establish the spatial distribution of flux, 
        $\phi_g(\vec{r})$ and temperature, $T(\vec{r})$ during transients.
        These distributions will give insight into MSFR behavior during
        transients, and identify potential risks that may warrant further
        study and changes to the fuel composition or the online fuel
        reprocessing scheme.
\end{abstract}

>>>>

In line with the purpose of the \gls{MSFR} as a thorium breeder, its chosen 
        start-up fuel composition is a eutectic mixture of $^{233}$U and 
        $^{232}$Th fluorides in a lithium fluoride molten salt 
        \cite{merle-lucotte_launching_2011}. We generate group constants for 
        each fuel composition using Serpent \cite{leppanen_serpent_2015}, a 
        continuous-energy Monte Carlo code for numerous reactor physics 
        applications. For verification, we will compare group constants and
        reactivity coefficients with existing data 
        \cite{fiorina_analysis_2012,fiorina_investigation_2013} of safety 
        parameters for the three fuel compositions.  
        Using these group constants ($\chi$, $\nu\Sigma_f$, 
        $\Sigma_{g\rightarrow g'}$, $\frac{d\rho}{dT}$, etc.), Moltres then 
        solves for the flux and temperature based on the neutron diffusion 
        equation coupled with navier stokes thermal hydraulics. Transient 
        simulations will establish the spatial distribution of flux, 
        $\phi_g(\vec{r})$ and temperature, $T(\vec{r})$ during transients.
        These distributions will give insight into MSFR transient behavior,
        which will help us identify potential safety risks.
        These risks may warrant further study and possibly, changes to the
        fuel composition or the online fuel reprocessing scheme.
\end{abstract}
